Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-11-09 paper/paper/SPIE/article.tex
make supplementary material

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{doi}
\usepackage{csquotes}
\MakeOuterQuote{"}

@@

\begin{table}[h!]
\caption{
    Feature groupings for summarization. eigs = non-RMT eigenfeatures and their combinations with
    other non-RMT eigenfeatures. rmt = RMT eigenfeatures and their combinations. tseries = baseline
    timeseries reductions.\\
}
\label{tab:features}
\small
\centering
\begin{tabular}{lllr}
\hline
\textbf{Gross Source} & \textbf{Feature Group} & \textbf{Feature id}   \\
\hline
eigs           & eigs          & \tcode{eigs}                           \\
               & eigs max      & \tcode{eigsminmax10}                   \\
               &               & \tcode{eigsminmax20}                   \\
               &               & \tcode{eigsminmax5}                    \\
               & eigs middle   & \tcode{eigsmiddle10}                   \\
               &               & \tcode{eigsmiddle20}                   \\
               &               & \tcode{eigsmiddle40}                   \\
               & eigs smooth   & \tcode{eigs + eigs\_smooth}            \\
               &               & \tcode{eigs + savgol}                  \\
               &               & \tcode{eigs\_savgol}                   \\
               &               & \tcode{eigs\_smooth}                   \\
               &               &                                        \\
rmt            & rmt + eigs    & \tcode{eigs + levelvar}                \\
               &               & \tcode{eigs + rigidity}                \\
               &               & \tcode{eigs + rigidity + levelvar}     \\
               &               & \tcode{eigs + unfolded}                \\
               &               & \tcode{eigs + unfolded + levelvar}     \\
               &               & \tcode{eigs + unfolded + rigidity}     \\
               & rmt only      & \tcode{levelvar}                       \\
               &               & \tcode{rigidity}                       \\
               &               & \tcode{rigidity + levelvar}            \\
               &               & \tcode{unfolded}                       \\
               &               & \tcode{unfolded + levelvar}            \\
               &               & \tcode{unfolded + rigidity}            \\
               &               & \tcode{unfolded + rigidity + levelvar} \\
               &               &                                        \\
tseries        & location      & \tcode{T-max}                          \\
               &               & \tcode{T-mean}                         \\
               &               & \tcode{T-med}                          \\
               &               & \tcode{T-min}                          \\
               &               & \tcode{T-p05}                          \\
               &               & \tcode{T-p95}                          \\
               & scale         & \tcode{T-iqr}                          \\
               &               & \tcode{T-rng}                          \\
               &               & \tcode{T-rrng}                         \\
               &               & \tcode{T-std}                          \\
\hline
\end{tabular}
\end{table}

@@

As there are a large number of figures, we summarize patterns of results across
two abstract levels of feature groupings—"gross", and "feature group"—shown in
Table \ref{tab:features}.

Finally, it makes sense to exclude classification tasks or an analytic
factor from summaries if there is no evidence that the classification task is
solvable in general, or for that factor. We take as lack of evidence of solvability
an mAUROC distribution that is either (1) roughly symmetric and has mean and median
very close to 0.5, or (2) left-tailed, with median less than 0.5.

\subsection{}

initial investigation reveals no evidence
that a certain compone

@@

\label{sec:results}

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6.5in]{gross_feature_overall_by_subgroup.png}
\end{tabular}
\end{center}
\caption
{ \label{fig:main-results}
AUROC distributions across gross feature groupings and comparison tasks.}
\end{figure}

>>>>

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{doi}
\usepackage{csquotes}
\MakeOuterQuote{"}
\usepackage{xr}
\externaldocument[S-]{supplementary}

@@

\begin{table}[h!]
\caption{
    Feature groupings for summarization. eigs = non-RMT eigenfeatures and their combinations with
    other non-RMT eigenfeatures. rmt = RMT eigenfeatures and their combinations. tseries = baseline
    timeseries reductions.\\
}
\label{tab:features}
\small
\centering
\begin{tabular}{lllr}
\hline
\textbf{Coarse Grouping} & \textbf{Fine Grouping} & \textbf{Feature id}   \\
\hline
eigs           & eigs          & \tcode{eigs}                           \\
               & eigs max      & \tcode{eigsminmax10}                   \\
               &               & \tcode{eigsminmax20}                   \\
               &               & \tcode{eigsminmax5}                    \\
               & eigs middle   & \tcode{eigsmiddle10}                   \\
               &               & \tcode{eigsmiddle20}                   \\
               &               & \tcode{eigsmiddle40}                   \\
               & eigs smooth   & \tcode{eigs + eigs\_smooth}            \\
               &               & \tcode{eigs + savgol}                  \\
               &               & \tcode{eigs\_savgol}                   \\
               &               & \tcode{eigs\_smooth}                   \\
               &               &                                        \\
rmt            & rmt + eigs    & \tcode{eigs + levelvar}                \\
               &               & \tcode{eigs + rigidity}                \\
               &               & \tcode{eigs + rigidity + levelvar}     \\
               &               & \tcode{eigs + unfolded}                \\
               &               & \tcode{eigs + unfolded + levelvar}     \\
               &               & \tcode{eigs + unfolded + rigidity}     \\
               & rmt only      & \tcode{levelvar}                       \\
               &               & \tcode{rigidity}                       \\
               &               & \tcode{rigidity + levelvar}            \\
               &               & \tcode{unfolded}                       \\
               &               & \tcode{unfolded + levelvar}            \\
               &               & \tcode{unfolded + rigidity}            \\
               &               & \tcode{unfolded + rigidity + levelvar} \\
               &               &                                        \\
tseries        & location      & \tcode{T-max}                          \\
               &               & \tcode{T-mean}                         \\
               &               & \tcode{T-med}                          \\
               &               & \tcode{T-min}                          \\
               &               & \tcode{T-p05}                          \\
               &               & \tcode{T-p95}                          \\
               & scale         & \tcode{T-iqr}                          \\
               &               & \tcode{T-rng}                          \\
               &               & \tcode{T-rrng}                         \\
               &               & \tcode{T-std}                          \\
\hline
\end{tabular}
\end{table}

@@

As there are a large number of figures, we summarize patterns of results across
two abstract levels of feature groupings—"coarse", and "fine"—shown in
Table \ref{tab:features}.

Finally, it makes sense to exclude classification tasks or an analytic factor
from summaries if there is no evidence that the classification task is solvable
in general, or for that factor. We take as lack of evidence of solvability an
mAUROC distribution that is either (1) roughly symmetric and has mean and
median close to 0.5, or (2) with median and mode less than 0.5.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6.5in]{coarse_feature_overall_by_subgroup.png}
\end{tabular}
\end{center}
\caption
{ \label{fig:main-results}
AUROC distributions across gross feature groupings and comparison tasks.}
\end{figure}

\subsection{Classification Tasks}

\subsubsection{Non-Predictable Comparisons}
Based on the mAUROC distributions for either coarsely-grouped (Figure
\ref{fig:main-results}) or finely-grouped features (Figure
S\ref{S-fig:feature-group-all}), neither bilinguality nor depression were
predictable by either baseline or eigenfeatures. Additionally, the \code{pain v
duloxetine} comparison in the \textit{Osteo} dataset, and the
\code{trait\_attend v trait\_nonattend} conditions ("WeeklyAttend" in Figures
\ref{fig:main-results} and S\ref{S-fig:feature-group-all}) in the \textit{Attention}
dataset were also not meaningfully predictable by any feature. As such, we exclude
these classification tasks from further figures and discussion.

\subsubsection{Predictable Comparisons}
As visible in Figure \ref{fig:main-results}, when coarsely summarizing features,
eigenfeatures were more likely to be predictively useful than not, and except
for in the \code{task\_attend v task\_nonattend} comparison, were also more
predictively useful than the baseline features. We also note that although
orders of magnitude more models were fit for eigenfeatures (see Section \ref{sec:multiverse}),
the mAUROC distributions for the baseline features are either equally as wide,
or, for the Parkinson's data, wider.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6.5in]{coarse_feature_by_preproc_predictive_subgroup.png}
\end{tabular}
\end{center}
\caption
{ \label{fig:preproc} mAUROC distributions by preprocessing degree.}
\end{figure}

\subsection{Effect of Preprocessing}
At a coarse level

@@
